Project 1 Checkpoint

### 2015-02-27 project1/checkpoint/main.tex
Cleaning a little

Given the difficulties with modelling we'll take a simpler approach and assume the ``true distribution`` is modeled by what was observed,
and simply plan to use the observed frequency distribution as our input distribution. As the project progresses we can
refine this model.

>>>>

Given the difficulties with modeling we'll take a simpler approach and assume the ``true distribution`` is modeled by what was observed,
and simply plan to use the observed frequency distribution as our input distribution.
